---
title: "simpleRegress"
author: "America Olivo"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```


```{r}
boxplot(WEIGHT~SEX,data=bears)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).


```{r}
lmWeight = lm(LENGTH ~ WEIGHT, data = bears) 
summary (lmWeight)
```




```{r}
lmNeck = lm(LENGTH ~ NECK, data = bears) 
summary (lmNeck)
```





```{r}
lnAgelm = lm(LENGTH ~ AGE, data = bears) 
summary (lnAgelm)
```




```{r}
lmChest = lm(LENGTH ~ CHEST, data = bears) 
summary (lmChest)
```


```{r}
lnHeadLen = lm(LENGTH ~ HEADLEN, data = bears) 
summary (lnHeadLen)
```


```{r}
lnHeadWth = lm(LENGTH ~ HEADWTH, data = bears)
summary(lnHeadWth)
```


1. head length and length
2. length and chest
3. length and neck 
4. length and weight
5. length and head width
6. length and age

